---
title: "MCI + Cancer: Preliminary Results"
author: "Magdalena Bennett"
date: "February 5th, 2021"
customjs: "macros.js"
output: 
  html_document:
    css: "style.css"
    toc: no
    beforeInit: "macros.js"
  pdf_document: 
    latex_engine: xelatex
    css: "style.css"
    toc: no
---
<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>

<style>
  @media screen and (min-width: 480px) {
    body {
      width: 90vw;
      height: 90vh;
    }

  div#main {
    font-size: 3vw;
    }
  }
</style>


# Introduction

- **Objective**: Compare Mild Cognitive Impairment (MCI) test score results over time between groups affected by cancer, either before or after their MCI diagnosis.

- We will be looking at both total MoCA scores and MoCA-MIS.

- To make both groups comparable, we will use an *stable balancing weighting* approach (Zubizarreta, 2015).

---

# Stable Balancing Weighting

- We focus on two different divisions: 
  
  (i) MCI vs MCI + Cancer, and
  
  (ii) MCI vs MCI + Cancer (before) vs MCI + Cancer (after)
  
  
- This means that the baseline or control group will be the **MCI group**.

- All groups are **unbalanced** a priori:

---

```{r echo = FALSE, message=FALSE}
library(htmltools)
library(paletteer)
library(reactable)
library(tidyverse)

tab1 <- read.csv("https://raw.githubusercontent.com/maibennett/website_github/master/exampleSite/content/results/cancer/balance_cancer.csv")
tab2 <- read.csv("https://raw.githubusercontent.com/maibennett/website_github/master/exampleSite/content/results/cancer/balance.csv")

before <- cbind(tab1$Cancer...MCI...Before, tab2$Cancer.Before...MCI, tab2$Cancer.After...MCI, tab1$MCI)

rownames(before) <- c("69-71 years","72-75 years","76-79 years","80 years or older","Female", "High school","Some college",
                              "College","Post-college")


colnames(before) <- c("MCI + Cancer (All)", "MCI + Cancer (Before Diag.)", "MCI + Cancer (After Diag.)", "MCI")

tbl <- before %>%
  reactable(
      # ALL one page (no scrolling or page swapping)
    pagination = TRUE,
    rownames = TRUE,
    # compact for an overall smaller table width wise
    compact = FALSE,
    # borderless - TRUE or FALSE
    borderless = FALSE,
    # Stripes - TRUE or FALSE
    striped = FALSE,
    # fullWidth - either fit to width or not
    fullWidth = TRUE,
    # apply defaults
    # 100 px and align to center of column
    defaultColDef = colDef(
      align = "center")
    )

div(
  # this class can be called with CSS now via .salary
  class = "before",
  div(
    # this can be called with CSS now via .title
    class = "title",
    h3("Average covariates by group before SBW")
  ),
  # The actual table
  tbl,
  # I use a span here so I can assigna  color to this text
  tags$span(style = "color:#C8C8C8", "TABLE: @maibennett")
)
  
```

<br>
<br>
- After re-weighting using SBW, **groups are now balanced with respect to the MCI group**:

---

```{r echo = FALSE, message=FALSE}
after <- cbind(tab1$Cancer...MCI...After, tab2$Cancer.Before...MCI.1, tab2$Cancer.After...MCI.1, tab1$MCI)

colnames(after) <- c("MCI + Cancer (All)", "MCI + Cancer (Before Diag.)", "MCI + Cancer (After Diag.)", "MCI")

rownames(after) <- c("69-71 years","72-75 years","76-79 years","80 years or older","Female", "High school","Some college",
                              "College","Post-college")

tbl <- after %>%
  reactable(
      # ALL one page (no scrolling or page swapping)
    pagination = TRUE,
    rownames = TRUE,
    # compact for an overall smaller table width wise
    compact = FALSE,
    # borderless - TRUE or FALSE
    borderless = FALSE,
    # Stripes - TRUE or FALSE
    striped = FALSE,
    # fullWidth - either fit to width or not
    fullWidth = TRUE,
    # apply defaults
    # 100 px and align to center of column
    defaultColDef = colDef(
      align = "center")
  )

div(
  # this class can be called with CSS now via .salary
  class = "after",
  div(
    # this can be called with CSS now via .title
    class = "title",
    h3("Average covariates by group after SBW")
  ),
  # The actual table
  tbl,
  # I use a span here so I can assigna  color to this text
  tags$span(style = "color:#C8C8C8", "TABLE: @maibennett")
)
  
```

# Preliminary Results

## MCI vs MCI + Cancer

Analyzing the MoCA and MoCA-MIS results grouped by year:

::: {.col data-latex="{0.47\textwidth}"}

```{r mocat_cancer, echo=FALSE, warning=FALSE, message = FALSE}
knitr::include_graphics("https://raw.githubusercontent.com/maibennett/website_github/master/exampleSite/content/results/cancer/mocat_cancer.svg")

```
:::

::: {.col data-latex="{0.06\textwidth}"}
\ 
<!-- an empty Div (with a white space), serving as
a column separator -->
:::

::: {.col data-latex="{0.47\textwidth}"}

```{r mocamis_cancer, echo=FALSE, warning=FALSE, message = FALSE}
knitr::include_graphics("https://raw.githubusercontent.com/maibennett/website_github/master/exampleSite/content/results/cancer/mocamis_cancer.svg")

```
:::
::::::


## MCI vs MCI + Cancer Before vs MCI + Cancer After

Analyzing the MoCA and MoCA-MIS results grouped by year:

::: {.col data-latex="{0.47\textwidth}"}

```{r mocat_cancer2, echo=FALSE, warning=FALSE, message = FALSE}
knitr::include_graphics("https://raw.githubusercontent.com/maibennett/website_github/master/exampleSite/content/results/cancer/mocat_cancer2.svg")

```
:::

::: {.col data-latex="{0.06\textwidth}"}
\ 
<!-- an empty Div (with a white space), serving as
a column separator -->
:::

::: {.col data-latex="{0.47\textwidth}"}

```{r mocamis_cancer2, echo=FALSE, warning=FALSE, message = FALSE}
knitr::include_graphics("https://raw.githubusercontent.com/maibennett/website_github/master/exampleSite/content/results/cancer/mocamis_cancer2.svg")

```
:::
::::::


# Survival Bias

- There is potential survival bias between the groups, given probabilities of death:

```{r echo = FALSE, message=FALSE}
deaths <- rbind(c("No",124,43,16),c("Yes",19,13,9))

colnames(deaths) <- c("Deaths","MCI","MCI + Cancer (Before)","MCI + Cancer (After)")


tbl <- deaths %>%
  reactable(
      # ALL one page (no scrolling or page swapping)
    pagination = TRUE,
    rownames = FALSE,
    # compact for an overall smaller table width wise
    compact = FALSE,
    # borderless - TRUE or FALSE
    borderless = FALSE,
    # Stripes - TRUE or FALSE
    striped = FALSE,
    # fullWidth - either fit to width or not
    fullWidth = TRUE,
    # apply defaults
    # 100 px and align to center of column
    defaultColDef = colDef(
      align = "center")
  )

div(
  # this class can be called with CSS now via .salary
  class = "deaths",
  div(
    # this can be called with CSS now via .title
    class = "title",
    h3("Number of deaths to date by group")
  ),
  # The actual table
  tbl,
  # I use a span here so I can assigna  color to this text
  tags$span(style = "color:#C8C8C8", "TABLE: @maibennett")
)
  
```

<br>
<br>
- While only **13% of the control MCI group** has died, over **23% of the group with MCI + Cancer before** the diagnosis passed away, and **36%** of the group who got a **cancer diagnosis after** MCI detection.