---
title: "MCI + Cancer: Preliminary Results"
author: "Magdalena Bennett"
date: "February 5th, 2021"
output: 
  html_document:
    css: style.css 
    toc: no
  pdf_document: 
    latex_engine: xelatex
    css: style.css
    toc: no
---

# Introduction

- **Objective**: Compare Mild Cognitive Impairment (MCI) test score results over time between groups affected by cancer, either before or after their MCI diagnosis.

- We will be looking at both total MoCA scores and MoCA-MIS.

- To make both groups comparable, we will use an *stable balancing weighting* approach (Zubizarreta, 2015).

---

# Stable Balancing Weighting

- We focus on two different divisions: 
  
  (i) MCI vs MCI + Cancer, and
  
  (ii) MCI vs MCI + Cancer (before) vs MCI + Cancer (after)
  
  
- This means that the baseline or control group will be the **MCI group**.


---

- All groups are **unbalanced** a priori:

```{r echo = FALSE, message=FALSE}
library(htmltools)
library(paletteer)
library(reactable)
library(tidyverse)

tab1 <- read.csv("https://raw.githubusercontent.com/maibennett/website_github/master/exampleSite/content/results/cancer/balance_cancer.csv")
tab2 <- read.csv("https://raw.githubusercontent.com/maibennett/website_github/master/exampleSite/content/results/cancer/balance.csv")

rownames(tab1) <- c("69-71 years","72-75 years","76-79 years","80 years or older","Female", "High school","Some college",
                              "College","Post-college")
rownames(tab2) <- c("69-71 years","72-75 years","76-79 years","80 years or older","Female", "High school","Some college",
                              "College","Post-college")


before <- cbind(tab1$Cancer...MCI...Before, tab2$Cancer.Before...MCI, tab2$Cancer.After...MCI, tab1$MCI)

colnames(before) <- c("MCI + Cancer (All)", "MCI + Cancer (Before Diag.)", "MCI + Cancer (After Diag.)", "MCI")

before %>%
  reactable(
      # ALL one page (no scrolling or page swapping)
    pagination = TRUE,
    # compact for an overall smaller table width wise
    compact = FALSE,
    # borderless - TRUE or FALSE
    borderless = FALSE,
    # Stripes - TRUE or FALSE
    striped = FALSE,
    # fullWidth - either fit to width or not
    fullWidth = TRUE,
    # apply defaults
    # 100 px and align to center of column
    defaultColDef = colDef(
      align = "center")
  )
  
```
- After re-weighting using SBW, **groups are now balanced with respect to the MCI group**:

```{r echo = FALSE, message=FALSE}
after <- cbind(tab1$Cancer...MCI...After, tab2$Cancer.Before...MCI.1, tab2$Cancer.After...MCI.1, tab1$MCI)

colnames(after) <- c("MCI + Cancer (All)", "MCI + Cancer (Before Diag.)", "MCI + Cancer (After Diag.)", "MCI")

after %>%
  reactable(
      # ALL one page (no scrolling or page swapping)
    pagination = TRUE,
    # compact for an overall smaller table width wise
    compact = FALSE,
    # borderless - TRUE or FALSE
    borderless = FALSE,
    # Stripes - TRUE or FALSE
    striped = FALSE,
    # fullWidth - either fit to width or not
    fullWidth = TRUE,
    # apply defaults
    # 100 px and align to center of column
    defaultColDef = colDef(
      align = "center")
  )
  
```

# Preliminary Results

<div style="width:1770px">
  <svg width="880" height="160" id="mocat_cancer"></svg>
  <svg width="880" height="160" id="mocamis_cancer">></svg>
</div>
