---
title: "STA 235H - Final Trivia" 
subtitle: "Fall 2023"
author: "McCombs School of Business, UT Austin"
output:
  xaringan::moon_reader:
    self_contained: true
    css: [xaringan-themer.css]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
      beforeInit: ["macros.js"]
    includes:
      in_header: ["header.html"]
---

<!-- <script type="text/javascript"> -->
<!-- MathJax.Hub.Config({ -->
<!--   "HTML-CSS": { -->
<!--     preferredFont: null, -->
<!--     webFont:  "Neo-Euler" -->
<!--   } -->
<!-- }); -->
<!-- </script> -->

```{r setup, include=FALSE, warning=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(fig.showtext = TRUE)
```

```{r xaringan-themer, include=FALSE, warning=FALSE, message=FALSE}
library(xaringanthemer)

theme_xaringan(
  text_color = "#333f48",
  background_color = "#FFFFFF",
  accent_color = "#900DA4",
  text_font = "Fira Mono",
  text_font_use_google = TRUE,
  title_font = "Yanone Kaffeesatz",
  title_font_use_google = TRUE
)

style_mono_accent(
  #base_color = "#bf5700",
  extra_fonts = list(google_font("Fira Sans","200","300","400","500","600"),
                     google_font("Fira Sans Condensed","200","300","400","500","600")),
  base_color = "#333f48",
  header_font_google = google_font("Yanone Kaffeesatz","200","300","400","500","600","700"),
  text_font_google   = google_font("Jost"),
  code_font_google   = google_font("Fira Mono"),
  text_bold_color = "#333f48",
  text_font_size = "115%",
  colors = c(
    lightgrey = "#C0C0C0",
    red = "#f34213",
    purple = "#900DA4",
    darkpurple = "#61077a",
    darkorange = "#db5f12",
    orange = "#ff8811",
    green = "#136f63",
    white = "#FFFFFF"),
  extra_css = list(
    ".remark-slide table" = list("display" = "table",
                   "width" = "80%",
                   "text-align" = "left"),
    ".remark-slide-number" = list("display" = "none"),
    ".strong" = list("font-weight" = "400"),
    ".big" = list("font-size" = "350%",
                     "font-family" = "Yanone Kaffeesatz",
                     "font-weight"="400"),
    ".small" = list("font-size" = "80%"),
    ".tiny" = list("font-size" = "70%"),
    ".large" = list("font-size" = "150%"),
    ".source" = list("color" = "#8c8c8c",
                     "font-size" = "80%"),
    ".remark-slide table td#highlight" = list("background-color" = "#eee1f0",
                                  "color" = "#900DA4",
                                  "font-weight" = "500"),
   # ".remark-slide table thead th" = list(),
    ".title-slide h1" = list("font-weight" = "500"),
    ".title-slide h2" = list("font-weight" = "400",
                             "font-size" =  "170%"),
    ".title-slide h3" = list("font-family" = "Jost",
                             "font-size" = "100%",
                             "font-weight" = "200"),
    ".center2" = list("margin" = "0",
                      "position" = "absolute",
                      "top" = "50%",
                      "left" = "50%",
                      "-ms-transform" = "translate(-50%, -50%)",
                      "transform" = "translate(-50%, -50%)"),
   ".bottom2" = list("margin" = "0",
                      "position" = "absolute",
                      "top" = "90%",
                      "left" = "10%",
                      "-ms-transform" = "translate(-10%, -90%)",
                      "transform" = "translate(-10%, -90%)"),
    ".section-title h1" = list("color" = "#FFFFFF",
                               "font-size" = "2.3em",
                               "line-height" = "1.3"),
    ".sp-after-half" = list("margin-bottom" = "0.7em !important"),
    ".box-1,.box-1a,.box-1s,.box-1b,.box-1l,.box-1LA,.section-title-1" = list("background-color" = "#0D0887"),
    ".box-2,.box-2a,.box-2s,.box-2b,.box-2l,.box-2LA,.section-title-2" = list("background-color" = "#5601A4"),
    ".box-3,.box-3a,.box-3s,.box-3b,.box-3l,.box-3LA,.section-title-3" = list("background-color" = "#900DA4"),
    ".box-4,.box-4a,.box-4s,.box-4b,.box-4l,.box-4LA,.section-title-4" = list("background-color" = "#BF3984"),
    ".box-5,.box-5a,.box-5s,.box-5b,.box-5l,.box-5LA,.section-title-5" = list("background-color" = "#E16462"),
    ".box-6,.box-6a,.box-6s,.box-6b,.box-6l,.box-6LA,.section-title-6" = list("background-color" = "#F89441"),
    ".box-7,.box-7a,.box-7s,.box-7b,.box-7l,.box-7LA,.section-title-7" = list("background-color" = "#FCCE25"),
   
    ".box-1trans,.box-2trans,.box-3trans,.box-4trans,.box-5trans,.box-6trans,.box-7trans" = list("background-color" = "#FFFFFF",
                                                                                                 "font-family" = "Yanone Kaffeesatz",
                                                                                                 "border-radius" = "15px",
                                                                                                 "margin" = "0em auto",
                                                                                                 "overflow" = "hidden",
                                                                                                 "padding" = "0.4em 0.4em",
                                                                                                 "font-weight" = "600",
                                                                                                 "font-size" = "31px",
                                                                                                 "display" = "table",
                                                                                                 "text-align" = "center",
                                                                                                 "border-width" = "thick",
                                                                                                 "color" = "#333f48"),
   
       ".box-1Trans,.box-2Trans,.box-3Trans,.box-4Trans,.box-5Trans,.box-6Trans,.box-7Trans" = list("background-color" = "#FFFFFF",
                                                                                                 "font-family" = "Yanone Kaffeesatz",
                                                                                                 "border-radius" = "15px",
                                                                                                 "margin" = "0em auto",
                                                                                                 "overflow" = "hidden",
                                                                                                 "padding" = "0.4em 0.4em",
                                                                                                 "font-weight" = "600",
                                                                                                 "font-size" = "51px",
                                                                                                 "display" = "table",
                                                                                                 "text-align" = "center",
                                                                                                 "border-width" = "thick",
                                                                                                 "color" = "#333f48"),
   
       ".box-1transl,.box-2transl,.box-3transl,.box-4transl,.box-5transl,.box-6transl,.box-7transl" = list("background-color" = "#FFFFFF",
                                                                                                           "font-family" = "Yanone Kaffeesatz",
                                                                                                           "border-radius" = "15px",
                                                                                                           "left" = "0px",
                                                                                                           "overflow" = "hidden",
                                                                                                           "padding" = "0.4em 0.4em",
                                                                                                           "font-weight" = "600",
                                                                                                           "font-size" = "31px",
                                                                                                           "display" = "table",
                                                                                                           "text-align" = "left",
                                                                                                           "border-width" = "thick",
                                                                                                           "color" = "#333f48"),
   
   
    ".box-1trans,.box-1transl,.box-1Trans" = list("border"="5px solid rgba(13, 8, 135,1)"),
    ".box-2trans,.box-2transl,.box-2Trans" = list("border"="5px solid rgba(86, 1, 164,1)"),
    ".box-3trans,.box-3transl,.box-3Trans" = list("border"="5px solid rgba(144, 13, 164,1)"),
    ".box-4trans,.box-4transl,.box-4Trans" = list("border"="5px solid rgba(191, 57, 132,1)"),
    ".box-5trans,.box-5transl,.box-5Trans" = list("border"="5px solid rgba(225, 100, 98,1)"),
    ".box-6trans,.box-6transl,.box-6Trans" = list("border"="5px solid rgba(248, 148, 65,1)"),
    ".box-7trans,.box-7transl,.box-7Trans" = list("border"="5px solid rgba(252, 206, 37,1)"),

   
   ".box-1t,.box-1tL,.section-title-1t" = list("background-color" = "rgba(13, 8, 135,0.3)",
                                      "color"="rgba(13, 8, 135,1)",
                                      "font-family" = "Yanone Kaffeesatz",
                                                                    "border-radius" = "15px"),
    ".box-2t,.box-2tL,.section-title-2t" = list("background-color" = "rgba(86, 1, 164,0.3)",
                                       "color" = "rgba(86, 1, 164,1)",
                                       "font-family" = "Yanone Kaffeesatz",
                                                                    "border-radius" = "15px"),
    ".box-3t,.box-3tL,.section-title-3t" = list("background-color" = "rgba(144, 13, 164,0.3)",
                                       "color" = "rgba(144, 13, 164,1)",
                                       "font-family" = "Yanone Kaffeesatz",
                                                                    "border-radius" = "15px"),
    ".box-4t,.box-4tL,.section-title-4t" = list("background-color" = "rgba(191, 57, 132,0.3)",
                                       "color" = "rgba(191, 57, 132,1)",
                                       "font-family" = "Yanone Kaffeesatz",
                                                                    "border-radius" = "15px"),
    ".box-5t,.box-5tL,.section-title-5t" = list("background-color" = "rgba(225, 100, 98,0.3)",
                                       "color" = "rgba(225, 100, 98,1)",
                                       "font-family" = "Yanone Kaffeesatz",
                                                                    "border-radius" = "15px"),
    ".box-6t,.box-6tL,.section-title-6t" = list("background-color" = "rgba(248, 148, 65,0.3)",
                                       "color" = "rgba(248, 148, 65,1)",
                                       "font-family" = "Yanone Kaffeesatz",
                                                                    "border-radius" = "15px"),
    ".box-7t,.box-7tL,.section-title-7t" = list("background-color" = "rgba(252, 206, 37,0.3)",
                                       "color" = "rgba(252, 206, 37,1)",
                                       "font-family" = "Yanone Kaffeesatz",
                                                                    "border-radius" = "15px"),
   
   ".box-7t, .box-6t, .box-5t, .box-4t, .box-3t, .box-2t, .box-1t" = list("margin" = "0em auto",
                                                                    "overflow" = "hidden",
                                                                    "padding" = "0.4em 0.4em",
                                                                    "font-weight" = "600",
                                                                    "font-size" = "31px",
                                                                    "display" = "table",
                                                                    "text-align" = "center",
                                                                    "border-radius" = "15px"),
   
   ".box-7tL, .box-6tL, .box-5tL, .box-4tL, .box-3tL, .box-2tL, .box-1tL" = list("margin" = "0em auto",
                                                                    "overflow" = "hidden",
                                                                    "padding" = "0.4em 0.4em",
                                                                    "font-weight" = "600",
                                                                    "font-size" = "50px",
                                                                    "display" = "table",
                                                                    "text-align" = "center",
                                                                    "border-radius" = "15px"),
   
    ".box-7, .box-6, .box-5, .box-4, .box-3, .box-2, .box-1" = list("color" = "#FFFFFF",
                                                                    "margin" = "0em auto",
                                                                    "overflow" = "hidden",
                                                                    "padding" = "0.4em 0.4em",
                                                                    "font-weight" = "600",
                                                                    "font-size" = "31px",
                                                                    "display" = "table",
                                                                    "text-align" = "center",
                                                                    "font-family" = "Fira Sans",
                                                                    "border-radius" = "15px"),
    ".box-7a, .box-6a, .box-5a, .box-4a, .box-3a, .box-2a, .box-1a" = list("color" = "#FFFFFF",
                                                                          "left" = "0px",
                                                                          "overflow" = "hidden",
                                                                      "padding" = "0.4em 0.4em",
                                                                      "font-weight" = "600",
                                                                      "font-size" = "25px",
                                                                      "display" = "table",
                                                                      "text-align" = "center",
                                                                      "font-family" = "Fira Sans",
                                                                    "border-radius" = "15px"),
   ".box-7s, .box-6s, .box-5s, .box-4s, .box-3s, .box-2s, .box-1s" = list("color" = "#FFFFFF",
                                                                          "left" = "0px",
                                                                          "overflow" = "hidden",
                                                                      "padding" = "0.2em 0.2em",
                                                                      "font-weight" = "400",
                                                                      "font-size" = "100%",
                                                                      "display" = "inline",
                                                                      "text-align" = "center",
                                                                      "font-family" = "Fira Sans",
                                                                    "border-radius" = "15px"),
       ".box-7b, .box-6b, .box-5b, .box-4b, .box-3b, .box-2b, .box-1b" = list("color" = "#FFFFFF",
                                                                          "left" = "0px",
                                                                          "overflow" = "hidden",
                                                                      "padding" = "0.4em 0.4em",
                                                                      "font-weight" = "600",
                                                                      "font-size" = "25px",
                                                                      "display" = "table",
                                                                      "text-align" = "left",
                                                                      "font-family" = "Fira Sans",
                                                                    "border-radius" = "15px"),
   ".box-7l, .box-6l, .box-5l, .box-4l, .box-3l, .box-2l, .box-1l" = list("color" = "#FFFFFF",
                                                                    "margin" = "0em auto",
                                                                    "overflow" = "hidden",
                                                                    "padding" = "0.4em 0.4em",
                                                                    "font-weight" = "600",
                                                                    "font-size" = "45px",
                                                                    "display" = "table",
                                                                    "text-align" = "center",
                                                                      "font-family" = "Yanone Kaffeesatz",
                                                                    "border-radius" = "15px"),
   ".box-7LA, .box-6LA, .box-5LA, .box-4LA, .box-3LA, .box-2LA, .box-1LA" = list("color" = "#FFFFFF",
                                                                    "margin" = "0em auto",
                                                                    "overflow" = "hidden",
                                                                    "padding" = "0.4em 0.4em",
                                                                    "font-weight" = "600",
                                                                    "font-size" = "55px",
                                                                    "display" = "table",
                                                                    "text-align" = "center",
                                                                      "font-family" = "Yanone Kaffeesatz",
                                                                    "border-radius" = "15px"),
   ".medium" = list("font-size" = "35px"),
   
   ".medium30" = list("font-size" = "30px"),
   
   ".jost-normal" = list("font-family" = "Jost",
                         "font-size" = "31px"),
   
   ".image-80 img" = list("scale" = "80%"),
   ".pull-left-little_l" = list("float" = "left",
                                "width" = "67%"),
   ".pull-right-little_l" = list("float" = "right",
                                "width" = "27%"),
   ".pull-left-little_r" = list("float" = "left",
                                "width" = "27%"),
   ".pull-right-little_r" = list("float" = "right",
                                "width" = "67%")


  )
)

#,"li" = list("font-size" = "150%")
#    "li" = list("font-size" = "110%"),
#    "ul" = list("font-size" = "110%"),
#color palette
#5601A4
#900DA4
#F89441
#FCCE25

knitr::opts_chunk$set(message = FALSE, warning = FALSE)

```
```{css, echo = FALSE}

.small .remark-code { /*Change made here*/
  font-size: 80% !important;
}

.tiny .remark-code { /*Change made here*/
  font-size: 80% !important;
}
```

```{r setup2, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(showtext)
library(xaringanExtra)
library(htmltools)
library(paletteer)
library(reactable)
library(htmlwidgets)
library(webshot2)
library(tidyverse)
library(extrafont)
library(hrbrthemes)
library(firasans)
library(kableExtra)
library(scales)
library(patchwork)
library(caret)
library(tidyverse)
library(estimatr)

# for windows
windowsFonts(sans = "Fira")
loadfonts(device="win")
loadfonts(device="postscript")

xaringanExtra::use_scribble()

htmltools::tagList(
  xaringanExtra::use_clipboard(
    button_text = "<i class=\"fa fa-clipboard\"></i>",
    success_text = "<i class=\"fa fa-check\" style=\"color: #90BE6D\"></i>",
    error_text = "<i class=\"fa fa-times-circle\" style=\"color: #F94144\"></i>"
  ),
  rmarkdown::html_dependency_font_awesome()
)
```

```{r fonts, message=FALSE, echo=FALSE, warning=FALSE}
font.add.google("Fira Sans Condensed", "Fira Sans Condensed")
font.add.google("Fira Sans", "Fira Sans")
```

# Rules of Final Trivia

1) **.darkorange[Form groups]**: 2 or 3 students (no more, no less).

--

2) **.darkorange[Choose a name for your group]**: You can be funny or classic.

--

3) **.darkorange[You need to complete all the questions]**: It doesn't matter if you don't know the answer! Make your best guess.

--

4) **.darkorange[Ask questions]**: I will give you time for your team to complete each questions; after the time is up, you will submit your questions and we will check answers.

  - If something isn't clear, **now is the time to ask**.

--

5) **.darkorange[There are prizes]**: At the end of the session, we will crown the teams that perform the best. If there is a tie in scores, the team that submits their answers the fastest moves up.

--


.center[**.darkorange[Note:]** All slides and answers will be posted on Wednesday at 4pm. Make sure to take notes!]

---
background-position: 50% 50%
class: left, bottom, inverse
.big[
Regressions
]
---
# Amazon prices

In this question, we are looking at luggage prices in Amazon US. We have data scraped from the website:

```{r, message=FALSE, warning=FALSE}
amz = read.csv("https://raw.githubusercontent.com/maibennett/website_github/master/exampleSite/content/files/data/amz_luggage.csv")

amz %>% select(-title) %>% head(.)
```

We want to find the association between covariates and the outcome (`price`).

---
# Question 1

.small[
```{r}
lm1 = lm(price ~ isBestSeller*stars, data = amz)

summary(lm1)
```
]

---
# Question 2

.small[
```{r}
lm1 = lm(price ~ isBestSeller*stars, data = amz)

summary(lm1)
```
]

---
# Question 3

.small[
```{r}
lm1 = lm(price ~ isBestSeller*stars, data = amz)

summary(lm1)
```
]


---
background-position: 50% 50%
class: left, bottom, inverse
.big[
Causal Inference
]
---
# Does Academic Probation Work?

Academic probation is a widely used tool by most universities to make sure students maintain minimum academic standards. In this section, we will analyze data from a large Canadian university regarding the effects of academic probation, originally used in Lindo, Sanders, and Oreopoulos’ (2010) paper, “Ability, Gender, and Performance Standards: Evidence from Academic Probation”

.tiny[
```{r, message=FALSE, warning=FALSE}
probation = read.csv("https://raw.githubusercontent.com/maibennett/website_github/master/exampleSite/content/files/data/probation.csv")
```
]
.pull-left[
.small[
- `creditsY`: Credits attempted in year Y = 1,2.
- `credits_earnedY`: Credits earned in year Y = 1,2.
- `GPA_yearY`: GPA at the end of year Y = 1,2.
- `CGPA_yearY`: Cumulative GPA at the end of year Y = 1,2.
- `sex`: Gender of the student (M: Male, F: Female).
- `age_at_entry`: Age of the student when they first enrolled.]]

.pull-right[
.small[
- `gradinY`: Student graduated in Y years, Y = 4, 5, or 6.
- `left_school`: Whether the student left school or not after the first assessment.
- `hsgrade_pct`: Percentile of graduation in their high school.
- `probation_year1`: Whether the student was in academic probation by the end of year 1.
- `suspended_year1`: Whether the student was suspended by the end of year 1.]]

---
# Question 4

.small[
```{r}
summary(lm_robust(left_school ~ probation_year1, data = probation))
```
]

---
# Question 5

.tiny[
```{r}
probation = probation %>% filter(left_school==0)

summary(lm(GPA_year2 ~ probation_year1 + credits1 + credits_earned1 + GPA_year1 + 
     factor(sex) + age_at_entry + hsgrade_pct, data = probation))

```
]

---
# Question 6

.tiny[
```{r}
probation = probation %>% filter(left_school==0)

summary(lm(GPA_year2 ~ probation_year1 + credits1 + credits_earned1 + GPA_year1 + 
     factor(sex) + age_at_entry + hsgrade_pct, data = probation))

```
]

---
background-position: 50% 50%
class: left, bottom, inverse
.big[
Prediction
]
---
# Candy, candy, candy

In this section, we will be predicting win percentage for candy bars! We have the following dataset for this:

.tiny[
```{r, message=FALSE, warning=FALSE}
candy = read.csv("https://raw.githubusercontent.com/maibennett/website_github/master/exampleSite/content/files/data/candy_r.csv")
```
]

.pull-left[
.small[
- `competitorname`:	Name of the candy
- `chocolate`: Is it chocolate?
- `fruity`: Is it fruit flavored?
- `caramel`: Is there caramel in the candy?
- `peanutalmondy`: Does it contain peanuts, peanut butter or almonds?
- `nougat`:	Does it contain nougat?
- `crispedricewafer`:	Does it contain crisped rice, wafers, or a cookie component?
]]

.pull-right[
.small[
- `hard`: Is it a hard candy?
- `bar`:	Is it a bar?
- `pluribus`: Is it one of many candies in a bag/box? 
- `sugarpercent`:	The percentile of sugar it falls under within the data set.
- `pricepercent`:	The unit price percentile compared to the rest of the set.
- `popularity`: How popular the candy is (3 levels).
- `winpercent`:	The overall win percentage according to 269,000 matchups.]]

---
# Question 7


```{r rd_linear, fig.height=5, fig.width=8, fig.align='center', dev='svg', echo=FALSE, warning=FALSE, message = FALSE}
library(rsample)
library(rpart)
library(rattle)
library(modelr)

set.seed(100)

candy = candy %>% select(-competitorname)

split = initial_split(candy, prop = 0.9, strata = "winpercent")
train.data = training(split)
test.data = testing(split)

set.seed(100)

dt = train(winpercent ~ ., data = train.data,
            method = "rpart",
            tuneGrid = expand.grid(cp = seq(0,0.1,length = 100)),
            trControl = trainControl(method = "cv", number = 10))

fancyRpartPlot(dt$finalModel, caption = "Decision Tree for Candy")
```

---
# Question 8

Access the code <u>[here](https://www.magdalenabennett.com/files/data/Trivia/f2023_sta235h_15_FinalTrivia.R)</u>

---
# Question 9

Access the code <u>[here](https://www.magdalenabennett.com/files/data/Trivia/f2023_sta235h_15_FinalTrivia.R)</u>
